Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 introduction.tex
Try to push a working version

With the newly developed techniques, we revisit the verification of quantum computation problem from both a philosophical and a practical point of view. 
Our first observation is that the sampling version of $\BQP$ (e.g., as formulated in Aaronson~\cite

>>>>

With the newly developed techniques, we revisit the classical verification of quantum computation problem from both a philosophical and a practical point of view. 
Our first observation is that the sampling version of $\BQP$ (e.g., as formulated by Aaronson~\cite{aaronson_2013})
